### 2020-06-30 2020/wada/adaptive_domain_adaptation.tex
correct some errors

Furthermore $ \varepsilon^k_{insep} < \varepsilon_{insep} $ which is the minimum of the error expectation over the hypothesis space of the classifier. With a trivial prediction $[\frac{1}{K},..,\frac{1}{K}]$ we have an error expectation equal to 0.5. Therefore, $\varepsilon_{insep} \leq 0.5$, i.e, $\varepsilon^k_{insep} < 0.5$. In the worst case where domains in the mixture are very close, we are still able to reduce the risk of predicting out-of-domain examples by a factor of 2.
\fyTodo{I sort of buy the equations but then so what ? We should may be compare with non-adaptive ?}

>>>>

\fyTodo{I sort of buy the equations but then so what ? We should may be compare with non-adaptive ?}
